\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors

### 2022-05-12 Manuscript/Lanuza_et_al_2021.Rmd
edits

Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018]. In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014]. Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions. Because the species' morphology can determine the species' functional role, an interesting novel approach to investigate plant-pollinator interactions is to examine how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016]. Thus, by defining the reproductive spectrum of trait variation is possible to investigate how the different reproductive strategies are associated worldwide with the interaction patterns of the different floral visitors.

[Keep from here](Jose)

>>>>

Although there is an increasing number of macroecological studies that investigate plant reproductive traits [@baude2016; @munoz2016; @grossenbacher2017; @moeller2017], we still have poor understanding of how reproductive traits drive interactions with floral visitors at large ecological scales [@sargent2008; @rech2016; @salguero2016; @ruger2018]. In addition, the pollination system of a great number of plant species remains unexplored and is still unclear how specific key reproductive traits like mating or compatibility system influence plant-pollinator associations [@tur2013; @devaux2014]. Interestingly, the use of trait-based approaches [@fenster2004; @rosas2014] and trait-matching analyses [@stang2009; @bartomeus2016] has shown to be of great importance when exploring the drivers of plant-pollinator interactions. Because the species' morphology can determine the species' functional role in the pollination network, an interesting novel approach to investigate plant-pollinator interactions is to examine how traits in the multidimensional trait space determine species interaction patterns [see @dehling2016]. Thus, by defining the reproductive spectrum of trait variation is possible to investigate how the different plant reproductive strategies are associated with the interaction patterns of the different floral visitors.

[Keep from here but remember to read again all coments, just in case I'm mssing something important](Jose)
